Supporting Information

### 2018-04-02 SupportingInformation.Rmd
various changes made

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")

seed<-101
families<-c(1,3:10,13,14,16:20)

source("mtime.R") #A function needed for caching
source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("normal_cop_AICw.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
source("TestStats_multivar_dataset.R")
source("skewness_multivar_dataset.R")
source("ExtremeTailDep.R")
source("mydispersal.R")
```

@@

<!--The copula looks like this:-->
```{r rankandplot_Loecke, echo=F, results='hide'}
#fig.cap="Copula plot of soil C and N data. Obtained by applying ranks separately to the C and N data, and then dividing the ranks by $n+1$ where $n$ is the number of sampling locations (see Sec. \ref{Model_selection}).\\label{fig_soilCNcop}",  fig.height=5, fig.width=5}

#convert to a copula and plot
pdf("./Results/SoilCNcop.pdf")
v_CN<-getcopula(d=d,rankon=T,ploton=T) 
dev.off()
```

@@

<!--The message=F and warning=F flags are to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a warning. Since anyway we want the independent copula, we can suppress the warning. We ran this
without the warning and it is OK to supress it.-->
<!-- The lines you are talking about appeared as message not as warning(actualy no warning appered for this chunk), so we have to set message=F here-->
```{r stat_testing_save_result, message=F, echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopupulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
set.seed(seed)

resultsloc<-"./Results/stat_results/stat_testing/"
spearvals<-seq(from=0,to=0.9,by=0.1)
callfn<-coplist_with_params(spearvals=spearvals)
coplist<-callfn$coplist
ncores<-3
res_pt35_rankF<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=F,mc.cores=ncores)
res_pt35_rankT<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=T,mc.cores=ncores)
res_pt1000_rankF<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=F,mc.cores=ncores)
res_pt1000_rankT<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=T,mc.cores=ncores)
save(res_pt35_rankF,res_pt35_rankT,res_pt1000_rankF,res_pt1000_rankT,file=paste(resultsloc,"StatTestNumericResults.RData",sep=''))
```

```{r stat_testing_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,callfn,mtime("StatTestNumericResults.RData"),mtime("TestStats_multivar_dataset.R"))}

@@

### Model selection approach \label{Ex_SoilCN_Model_selection}
<!--This does the computations for this section-->
```{r bivmodselect_Loecke, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"))}
set.seed(seed)
families_Loecke<-c(1,3:10,13:14,16:20) 
BivMS_res_Loecke<-OurBiCopSelect(u1=v_CN[,1],u2=v_CN[,2],families=families_Loecke,level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
```

@@

### Non-parametric analysis of tail dependence \label{Ex_SoilCN_NPA}
<!--Do the intensive part of the analysis, calculating stats on the data and surrogates-->
```{r stat_soilCN_graphic_approach, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)

@@

<!--Load the raw data-->
```{r read_aphid_data, echo=F}
# Aphid raw data for count
d0_count<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidtscount141117.csv",header=F))
data_aphid_count<-d_allsp_data(d0_count)

@@

<!--Do the calculations-->
```{r RES_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("FittingCopula_selective_loc.R"))}
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_aphid_count<-RES_single_sp(d_allsp=data_aphid_count,sp=10,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
#cat(paste("stop-time: ",Sys.time(),"\n"))
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_count,paste(resloc,file="AphidCopulaFit_selecloc_count_species_10.RDS",sep=""))
```

@@

```{r tab_count_AICw_normal, echo=F, results='markup'}
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_count),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for abundances of the green spruce aphid, for comparison with Table \\ref{tab_count_AICw}. \\label{tab_count_AICw_normal}",
             booktabs=TRUE
             )
```

@@

<!--Do the main computations for this section-->
```{r stat_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("NonParamStat.R"))}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_aphid_count/"

@@

<!--Do the analysis-->
```{r RES_aphid_ff, echo=F, cache=T, cache.extra=list(seed,data_aphid_ff,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("FittingCopula_selective_loc.R"))} 
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n"))
RES_aphid_ff<-RES_single_sp(d_allsp=data_aphid_ff,sp=11,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
#cat(paste("stop-time: ",Sys.time(),"\n")) 
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_ff,paste(resloc,file="AphidCopulaFit_selecloc_firstflight_species_11.RDS",sep=""))
```

@@

```{r tab_ff_AICw_normal, echo=F, results='markup'}
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_ff),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for first flight data for the leaf-curlung plum aphid, for comparison with Table \\ref{tab_ff_AICw}.\\label{tab_ff_AICw_normal}",
             booktabs=TRUE
             )
```

@@

<!--Do the analysis-->
```{r stat_aphid_ff, echo=F, cache=T, cache.extra=list(seed,data_aphid_ff,mtime("NonParamStat.R"))}
set.seed(seed)
resloc<-"./Results/stat_results/stat_aphid_ff/"

@@

<!--Load the data-->
```{r read_plankton_north_sea_data, echo=F}
d0_plankton_north_sea<-as.matrix(read.csv("./Data/Plankton_North_Sea_data/planktontimeseries201117_4.csv",header=F))
data_plankton_north_sea<-d_allsp_data_plankton_north_sea(d0_plankton_north_sea)
```

<!--Do the main analysis-->
```{r RES_plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"), mtime("FittingCopula_selective_loc.R"))}

@@

```{r tab_pns_AICw_normal,echo=F,results="markup"}
knitr::kable(normal_cop_AICw_matrix(r=RES_plankton_north_sea),
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : AICw for 'Normal' copula family for each selective location pair\\label{tab_pns_AICw_normal}",
             booktabs=TRUE)
```

@@

### Non-parametric analysis of tail dependence  \label{Ex_pns_NPA}
```{r stat_plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("NonParamStat.R"))}
set.seed(seed)
resloc<-"./Results/stat_results/stat_plankton_north_sea/"

@@

```{r skewness_count_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_count,sp=10,data_pt_thrs=30)
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

```{r skewness_ff_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_ff,sp=11,data_pt_thrs=30)

@@

```{r skewness_pns_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=16,data_pt_thrs=45)
answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

### LC model :
```{r fig_risk_r0_numlocs5, echo=F, cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0_numlocs5}", fig.height=3.5, fig.width=8}
set.seed(seed)
varying_d(numsims=10000,numsteps =25,numlocs=5,r=0,K=50,disp_everywhere=F)
```

@@

```{r fig_risk_r0.05, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

@@

```{r fig_risk_r0.05_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

@@

<!--do a TL analysis on the data just created-->
```{r tl_analysis, echo=F, cache=T, cache.extra=list(mtime("TaylorsLawTools.R"),seed,mtime("copsurrognd.R"))}
source("TaylorsLawTools.R")
# 
# #We are only doing spatial taylor's law because we know a priori temporal
# #won't give anything interesting for the surrogates we use
# 
 kend.stats.res<-list()
 kend.points.res<-list()
 spea.stats.res<-list()
 spea.points.res<-list()
 for (counter in 1:length(kend.surrog))
 {
   ks<-kend.surrog[[counter]]
   ss<-spea.surrog[[counter]]
   kend.stats.res[[counter]]<-matrix(NA,5,numdat)
   spea.stats.res[[counter]]<-matrix(NA,5,numdat)
   kend.points.res[[counter]]<-array(NA,c(N,2,numdat))
   spea.points.res[[counter]]<-array(NA,c(N,2,numdat))
   for (sc in 1:numdat)
   {
     khold<-tl_stats(ks[,,sc])
     kend.stats.res[[counter]][,sc]<-khold$s.stats #spatial TL only
     rownames(kend.stats.res[[counter]])<-names(khold$s.stats)
     kend.points.res[[counter]][,,sc]<-as.matrix(khold$s.points)
# 
     shold<-tl_stats(ss[,,sc])
     spea.stats.res[[counter]][,sc]<-shold$s.stats #spatial TL only
     rownames(spea.stats.res[[counter]])<-names(shold$s.stats)
     spea.points.res[[counter]][,,sc]<-as.matrix(shold$s.points)
   }
 }
 names(kend.stats.res)<-names(kend.surrog)
 names(kend.points.res)<-names(kend.surrog)
 names(spea.stats.res)<-names(spea.surrog)
 names(spea.points.res)<-names(spea.surrog)
```

>>>>

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
# families<-c(1,3:10,13,14,16:20)
source("mtime.R") #A function needed for caching
```

@@

<!--The copula looks like this:-->
```{r rankandplot_Loecke, echo=F, results='hide'}
#fig.cap="Copula plot of soil C and N data. Obtained by applying ranks separately to the C and N data, and then dividing the ranks by $n+1$ where $n$ is the number of sampling locations (see Sec. \ref{Model_selection}).\\label{fig_soilCNcop}",  fig.height=5, fig.width=5}
source("getcopula.R")
#convert to a copula and plot
pdf("./Results/SoilCNcop.pdf")
v_CN<-getcopula(d=d,rankon=T,ploton=T) 
dev.off()
```

@@

<!--The message=F and warning=F flags are to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a warning. Since anyway we want the independent copula, we can suppress the warning. We ran this
without the warning and it is OK to supress it.-->
<!-- The lines you are talking about appeared as message not as warning(actualy no warning appered for this chunk), so we have to set message=F here-->
```{r stat_testing_save_and_plot_result, message=F, echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
source("TestStats_multivar_dataset.R")
set.seed(seed)

resultsloc<-"./Results/stat_results/stat_testing/"
spearvals<-seq(from=0,to=0.9,by=0.1)
callfn<-coplist_with_params(spearvals=spearvals)
coplist<-callfn$coplist
ncores<-3
res_pt35_rankF<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=F,mc.cores=ncores)
res_pt35_rankT<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=T,mc.cores=ncores)
res_pt1000_rankF<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=F,mc.cores=ncores)
res_pt1000_rankT<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=T,mc.cores=ncores)
save(res_pt35_rankF,res_pt35_rankT,res_pt1000_rankF,res_pt1000_rankT,file=paste(resultsloc,"StatTestNumericResults.RData",sep=''))

@@

### Model selection approach \label{Ex_SoilCN_Model_selection}
<!--This does the computations for this section-->
```{r bivmodselect_Loecke, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("OurBiCopSelect.R")
set.seed(seed)
families_Loecke<-c(1,3:10,13:14,16:20) 
BivMS_res_Loecke<-OurBiCopSelect(u1=v_CN[,1],u2=v_CN[,2],families=families_Loecke,level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
```

@@

### Non-parametric analysis of tail dependence \label{Ex_SoilCN_NPA}
<!--Do the intensive part of the analysis, calculating stats on the data and surrogates-->
```{r stat_soilCN_graphic_approach, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
source("CopulaFunctions_flexible.R")
source("copsurrog2d.R")
set.seed(seed)

@@

<!--Load the raw data-->
```{r read_aphid_data, echo=F}
source("aphid_data_calling.R")

# Aphid raw data for count
d0_count<-as.matrix(read.csv("./Data/Aphid_data/APHID_DATA_RAW/aphidtscount141117.csv",header=F))
data_aphid_count<-d_allsp_data(d0_count)

@@

<!--Do the calculations-->
```{r RES_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}

source("FittingCopula_selective_loc.R")  # top most hierarchy source file
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n")) 
RES_aphid_count<-RES_single_sp(d_allsp=data_aphid_count,sp=10,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
#cat(paste("stop-time: ",Sys.time(),"\n"))
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_count,paste(resloc,file="AphidCopulaFit_selecloc_count_species_10.RDS",sep=""))
```

@@

```{r tab_count_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_count),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for abundances of the green spruce aphid, for comparison with Table \\ref{tab_count_AICw}. \\label{tab_count_AICw_normal}",
             booktabs=TRUE
             )
```

@@

<!--Do the main computations for this section-->
```{r stat_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

source("good_loclist.R")
source("NonParamStat.R")
set.seed(seed) 
resloc<-"./Results/stat_results/stat_aphid_count/"

@@

<!--Do the analysis-->
```{r RES_aphid_ff, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}

source("FittingCopula_selective_loc.R")  # top most hierarchy source file
set.seed(seed)
#cat(paste("start-time: ",Sys.time(),"\n"))
RES_aphid_ff<-RES_single_sp(d_allsp=data_aphid_ff,sp=11,families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30)
#cat(paste("stop-time: ",Sys.time(),"\n")) 
resloc<-"./Results/fitting_results/"
saveRDS(RES_aphid_ff,paste(resloc,file="AphidCopulaFit_selecloc_firstflight_species_11.RDS",sep=""))
```

@@

```{r tab_ff_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_ff),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for first flight data for the leaf-curlung plum aphid, for comparison with Table \\ref{tab_ff_AICw}.\\label{tab_ff_AICw_normal}",
             booktabs=TRUE
             )
```

@@

<!--Do the analysis-->
```{r stat_aphid_ff, echo=F, cache=T,  cache.extra=list(seed,data_aphid_ff,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

source("good_loclist.R")
source("NonParamStat.R")
set.seed(seed)
resloc<-"./Results/stat_results/stat_aphid_ff/"

@@

<!--Load the data-->
```{r read_plankton_north_sea_data, echo=F}
source("plankton_north_sea_data_calling.R")
d0_plankton_north_sea<-as.matrix(read.csv("./Data/Plankton_North_Sea_data/planktontimeseries201117_4.csv",header=F))
data_plankton_north_sea<-d_allsp_data_plankton_north_sea(d0_plankton_north_sea)
```

<!--Do the main analysis-->
```{r RES_plankton_north_sea, echo=F, cache=T, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}

source("FittingCopula_selective_loc.R")  # top most hierarchy source file

@@

```{r tab_pns_AICw_normal,echo=F,results="markup"}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_plankton_north_sea),
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : AICw for 'Normal' copula family for each selective location pair\\label{tab_pns_AICw_normal}",
             booktabs=TRUE)
```

@@

### Non-parametric analysis of tail dependence  \label{Ex_pns_NPA}
```{r stat_plankton_north_sea, echo=F, cache=T, cache=T,  cache.extra=list(seed,data_plankton_north_sea,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

source("good_loclist.R")
source("NonParamStat.R")
set.seed(seed)
resloc<-"./Results/stat_results/stat_plankton_north_sea/"

@@

```{r skewness_count_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

source("good_loclist.R")
source("skewness_multivar_dataset.R")
set.seed(seed)

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_count,sp=10,data_pt_thrs=30)
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

```{r skewness_ff_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,data_aphid_ff,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

source("good_loclist.R")
source("skewness_multivar_dataset.R")
set.seed(seed)

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_ff,sp=11,data_pt_thrs=30)

@@

```{r skewness_pns_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

source("good_loclist.R")
source("skewness_multivar_dataset.R")
set.seed(seed)

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=16,data_pt_thrs=45)
answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

### LC model :
```{r fig_risk_r0_numlocs5, echo=F, cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0_numlocs5}", fig.height=3.5, fig.width=8}
source("mydispersal.R")
set.seed(seed)
varying_d(numsims=10000,numsteps =25,numlocs=5,r=0,K=50,disp_everywhere=F)
```

@@

```{r fig_risk_r0.05, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05}", fig.height=3.5, fig.width=8}
source("mydispersal.R")
set.seed(seed)
r<-0.05
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

@@

```{r fig_risk_r0.05_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05_disp_everywhere}", fig.height=3.5, fig.width=8}
source("mydispersal.R")
set.seed(seed)
r<-0.05
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

@@

<!--do a TL analysis on the data just created-->
```{r tl_analysis, echo=F, cache=T, cache.extra=list(mtime("TaylorsLawTools.R"),seed,mtime("copsurrognd.R"))}
source("copsurrognd.R")
source("TaylorsLawTools.R")
# 
# #We are only doing spatial taylor's law because we know a priori temporal
# #won't give anything interesting for the surrogates we use
# 
 kend.stats.res<-list()
 kend.points.res<-list()
 spea.stats.res<-list()
 spea.points.res<-list()
 for (counter in 1:length(kend.surrog))
 {
   ks<-kend.surrog[[counter]]
   ss<-spea.surrog[[counter]]
   kend.stats.res[[counter]]<-matrix(NA,5,numdat)
   spea.stats.res[[counter]]<-matrix(NA,5,numdat)
   kend.points.res[[counter]]<-array(NA,c(N,2,numdat))
   spea.points.res[[counter]]<-array(NA,c(N,2,numdat))
   for (sc in 1:numdat)
   {
     khold<-tl_stats(ks[,,sc])
     kend.stats.res[[counter]][,sc]<-khold$s.stats #spatial TL only
     rownames(kend.stats.res[[counter]])<-names(khold$s.stats)
     kend.points.res[[counter]][,,sc]<-as.matrix(khold$s.points)
# 
     shold<-tl_stats(ss[,,sc])
     spea.stats.res[[counter]][,sc]<-shold$s.stats #spatial TL only
     rownames(spea.stats.res[[counter]])<-names(shold$s.stats)
     spea.points.res[[counter]][,,sc]<-as.matrix(shold$s.points)
   }
 }
 names(kend.stats.res)<-names(kend.surrog)
 names(kend.points.res)<-names(kend.surrog)
 names(spea.stats.res)<-names(spea.surrog)
 names(spea.points.res)<-names(spea.surrog)
```
